Data Exploration

### 2019-02-24 src/stack_test.Rmd
...

messing with code to see if can do for unique year month depth
```{r}
ascname <- list.files("../data/jan_test_86.9/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks
rasters <- lapply(paste0(ascname), raster)

@@

  }
   # st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
#st19980186.9
```

>>>>

This works

```{r}
ascname <- list.files("../data/jan_test_86.9/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks
rasters <- lapply(paste0(ascname), raster)

@@

  }
   st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
st19980186.9
```

messing with code to see if can do for unique year month depth

need tidyr package
```{r}
unyears <- as.character(c(1992, 1998)) 
x <- "X"
unyears <- paste0(x, unyears, collapse = NULL) #this adds an X to each year to match with raster naming
unmonths <- c(01, 03)
undepths <- c(10, 86.9294)

unlayer <- crossing(unyears, unmonths, undepths)

for (uny in unyears){
  for (unm in unmonths){
    for (und in undepths){
      year <- unyears[uny]
      month <- unmonths[unm]
      depth <- undepths[und]
    }
  }
}

ascname <- list.files("../data/jan_test_86.9/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks
rasters <- lapply(paste0(ascname), raster)

  }
   # st19980186.9 <- stack(temp_depth, chl_surface, o2_depth, salinity_depth, nao_sample, nao_winter)
  }
#st19980186.9
